%% OTP_Abstract.tex
%% Abstract: must NOT exceed one single-spaced page.
%% Must identify all priorities being addressed (AP1-AP3 and CPP1).
\documentclass[12pt,letterpaper]{article}
\usepackage{../otpgrant}

\begin{document}
\singlespacing
\pagestyle{empty} % one page; no page number needed

\begin{center}
  {\bfseries Project Abstract}\\
  Open Textbook Pilot Program (84.116T), FY 2026\\
  \emph{Ximera: Interactive Mathematics Education Resources for All}
\end{center}

\noindent\textbf{Lead applicant:} The Ohio State University.

\noindent\textbf{Consortium partners:} University of Florida, Lakeland
Community College, Oregon State University, and Prairie View A\&M
University. Employer and professional-association partners include
Infonomic, BAWL (Botting Accessibility with \LaTeX), SageMath, and Desmos.

\noindent\textbf{Absolute Priority 1 (Improving Collaboration and
Dissemination):} The five-institution Ximera Consortium will develop
ATLAS (Activity Topic Library And Social), an open discovery and
dissemination platform that connects instructors at any institution to LMS-ready Ximera activities via Modulus, the project's
LTI~1.3 grade-passback system. Collaboration tools are built into Ximera's design. Annual workshops will be held.


\noindent\textbf{Absolute Priority 2 (Addressing Gaps and Bringing
Solutions to Scale):} The open textbook marketplace lacks any solution
combining interactive instruction, integrated homework, LMS grade
passback, and WCAG~2.1~AA accessibility into a single environment.
Ximera closes each gap with a client-side interactive platform, a
robust algebraic answer-checker, and a clear path to full WCAG~2.1~AA
compliance ahead of the April~2027 federal deadline. 

\noindent\textbf{Absolute Priority 3 (Promoting Student Success):}
Ximera currently serves approximately 35,000 students annually across
14 institutions, generating around \$4.13~million in annual savings. OTP Phase~II will scale savings
to at least \$7~million per year by Year~4. Popular math OER materials written in \LaTeX\ will be converted to Ximera.  



\noindent\textbf{Competitive Preference Priority 1 (Advancing
Artificial Intelligence in Education):} This application explicitly
addresses Competitive Preference Priority~1 (91~FR~18774). OTP
Phase~I integrated HaLLMos AI chat into Ximera, giving students
immediate AI-guided feedback on free-response questions. OTP Phase~II
will add: AI-powered ``ask me another'' prompting for students;
LLM-assisted content authoring based on prompts and pictures; and Modulus-derived AI data dashboards for instructors.

\noindent\textbf{Target population:} Undergraduate students in
high-enrollment gateway mathematics courses; faculty and instructors at
two-year colleges, regional universities, and research universities;
and the institutions serving them.

\noindent\textbf{Project objectives and activities (48-month
performance period):} Deploy ATLAS for content discovery and one-click
LMS connection; extend Modulus to Canvas, Blackboard, and
Brightspace; achieve WCAG~2.1~AA compliance across all content;
complete the Stitz-Zeager Precalculus conversion; continue Flash
Grants ($\sim$32 awards/year), annual Ximera Workshops, and monthly
Office Hours; and pilot a subscription-consultation sustainability
model by Year~4.

\noindent\textbf{Project outcomes:} Enrollment growing from 35,000 to
55,000 annual students; e\$7~million in annual savings by Year~4
total student savings of \$23.5~million over the project period.

\noindent\textbf{Projected average cost savings per student:}
\$120--\$125.

\noindent\textbf{Projected total cost savings (48-month performance
period):} \$23,550,000.

\end{document}