%% OTP_Budget_Narrative.tex
%% Budget Narrative -- not counted toward the narrative page limit.
%% Must itemize every project year; per-year totals must match
%% SF-424A Section E, and the four-year total must match Section A line 5(e).
\documentclass[12pt,letterpaper]{article}
\usepackage{../otpgrant}
\usepackage{todonotes}
% [disable] to hide all

\title{\bfseries Budget Narrative\\[0.5ex]
  \large Open Textbook Pilot Program (84.116T), FY 2026}
\author{The Ohio State University}
\date{}

% One environment per project year; categories mirror the SF-424A
% object class categories and the notice's required breakdown.
\newcommand{\budgetyear}[1]{\section{Project Year #1}}
\newcommand{\budgetcat}[1]{\subsection*{#1}}

\begin{document}
\singlespacing % the double-spacing standard applies to the narrative;
               % budget narratives are conventionally single-spaced.

\maketitle
\thispagestyle{empty}
\clearpage

\budgetyear{1}
\budgetcat{Personnel (\$62,837)}
  \paragraph{Bart Snapp, Principal Investigator}  (course release: \$19,219). Dr.\ Snapp is an Associate Professor of Teaching-Practice in the Department of Mathematics at The Ohio State University. He is currently the Director of the Ximera  project. He will continue to provide overall project direction, coordinate consortium activities, oversee dissemination efforts, manage Flash Grant awards, direct development of AI-assisted authoring tools for Ximera content creation, and ensure alignment with grant objectives. One course release per year in Years 1 and 2 will allow dedicated time for project leadership during the critical startup phase of the new award. The course release rate is based on OSU's standard buyout calculation.
  \paragraph{Jim Fowler, Co-Investigator}  (2 months summer support: \$29,625). Dr.\ Fowler is an Associate Professor and Vice Chair for Undergraduate Studies
in the Department of Mathematics at The Ohio State University and the lead backend developer for Ximera. During two months of summer support each year, Dr.\ Fowler will focus on platform development, including improvements to the Ximera server architecture, server-side infrastructure for LLM integration, and coordination with Infonomic on Modulus development. The summer salary is calculated at the current monthly rate of \$14,812.67.
  \paragraph{Elizabeth Miller, Evaluator}  (\$7,740). Ms.\ Miller is an Instructional Designer within Mathematics and Statistics Learning Center at The Ohio State University. She will collect and analyze performance data from consortium institutions, including enrollment figures, completion rates, DFW rates, and GPA comparisons. She will distribute and compile surveys to Ximera-adopting institutions each semester and maintain the project's longitudinal dataset. Compensation is based on her current annual salary of \$89,481 at a level of effort proportional to the scope of work.
  \paragraph{Carolyn Johns, Evaluator} (\$6,252). Dr.\ Johns is the Interim Director of the Mathematics and Statistics Learning Center at The Ohio State University. She will work alongside Ms.\ Miller on data collection, institutional outreach, and survey administration. She will focus on coordinating responses from new consortium partners and tracking course-level adoption metrics. Compensation is based on her current annual salary of \$72,281 at a level of effort proportional to the scope of work.
% List each position by title; role, annual salary, % effort, amount charged.
% 
\budgetcat{Fringe Benefits (\$15,185)}

Fringe benefits are calculated using OSU's federally negotiated rates: 15.8\% for off-duty (summer) faculty appointments applied to Dr.\ Fowler's summer salary (\$4,681); 28.3\% for regular faculty applied to Dr.\ Snapp's course release (\$5,439); and 36.2\% for Administrative and Professional (A\&P) staff applied to Ms.\ Miller and Dr.\ Johns (\$5,065).

\budgetcat{Travel (\$46,000)}
% Grantee staff only: purpose, # travelers, trips, per diem, mileage.
% include exactly where you will go as specifically as you can.
Travel funds support dissemination and consortium-building activities at approximately \$2,000 per person-trip, covering airfare, lodging, per diem, and registration fees. At this rate, the budget supports approximately 23 person-trips per year. Anticipated travel includes attendance and exhibition at four major national or international mathematics and education conferences (such as the Joint Mathematics Meetings, MAA MathFest, AMATYC, and the Mathematical Congress of the Americas), as well as travel to support one annual Ximera Workshop for hands-on training of new and existing authors. Conference attendance provides critical visibility for the project, enables direct recruitment of new consortium institutions, and supports dissemination of best practices for open textbook adoption. The Dissemination Specialist (see Other) will identify additional conference opportunities throughout the year.


\budgetcat{Equipment (\$0)}

No equipment purchases are anticipated.

\budgetcat{Supplies (\$6,000)}

Year 1 supplies include any hardware required by developers,  printed Ximera User Manuals, promotional materials (t-shirts, stickers, branded items), and booth display materials for use at conference exhibitions. The higher Year 1 amount reflects one-time costs for initial production of booth banners, signage, and display stands that will be reused in subsequent years.

% Tangible property under $10,000/unit; list item, quantity, unit cost.
\budgetcat{Contractual (\$0)}

All consultant and contract costs are reported under Other (line 6h), as these arrangements are structured as independent service agreements rather than formal procurements through OSU's institutional contracting system.
% Procurement-system contracts; consultant fees/expenses/travel under contract.


\budgetcat{Construction (\$0)}
No construction is proposed.

\budgetcat{Other (\$225,000)}


\paragraph{Contract: BAWL (Botting Accessibility With \LaTeX), Jeff Kuan (\$50,000).} Mr.\ Kuan is the accessibility specialist for the Ximera project and operates BAWL, a consultancy dedicated to accessible STEM content. He will ensure that all Ximera materials and platform features meet WCAG 2.1 Level AA compliance, author and maintain the accessibility sections of the Ximera User Manual, conduct accessibility audits of new and existing content, and coordinate with Neil Soiffer (MathCAT) on mathematical screen reader compatibility. This contract reflects the specialized, ongoing nature of accessibility work across a growing corpus of open materials serving tens of thousands of students.

\paragraph{Contract: Infonomic (\$100,000).} Infonomic (infonomic.io) is the contractor developing Modulus, the Ximera project's LTI 1.3--compliant assignment-grade database. In Year 1, Infonomic will confirm completeness of the minimum viable product, conduct integration testing with Canvas LMS installations at OSU and the University of Florida, and begin onboarding consortium partners. Moreover, Infonomic will begin work on the Modulus Atlas Dissemination Platform. The higher Year 1 amount reflects the intensive development work required to bring Modulus to production readiness. 

\paragraph{Contract: Wim Obbels, DevOps (\$12,000).} Mr.\ Obbels (KU Leuven) maintains the Docker-based Ximera server infrastructure, the authoring and compilation environment, and deployment tooling. At \$1,000 per month, this contract provides ongoing server administration, security updates, and technical support for institutions deploying their own Ximera servers.

\paragraph{Contract: Paul Zachlin, Dissemination Specialist (\$5,000).} Dr.\ Zachlin is a Professor of Mathematics at Lakeland Community College, a co-author of the Ximera Linear Algebra textbook, and the 2026 recipient of the Carol Crawford Excellence in Undergraduate Teaching Award from the Ohio MAA. He will serve as the project's Dissemination Specialist, identifying conference presentation opportunities throughout the year, coordinating Ximera representation at regional and national meetings (including AMATYC, state MAA sections, and discipline-specific venues), and assisting the PI in recruiting presenters from across the consortium. Dr.\ Zachlin's extensive network across two-year and four-year institutions, and his active conference participation, make him uniquely positioned to extend the project's reach beyond research universities.

\paragraph{Flash Grant Stipends (\$54,000).} Flash Grants are small awards ranging from \$400 to \$4,000 that support Ximera content adoption, development, and improvement across consortium institutions and beyond. At an estimated average of approximately \$1,700 per award, this budget supports roughly 32 Flash Grants per year. Examples of fundable activities at the \$400 level include: creating 2 videos or interactive elements and embedding them into a Ximera assignment; creating 1--3 chapters of a course in the Ximera document class; adding interactives to 1--3 chapters of an existing PDF-based course; reviewing or editing one-third of an online course; creating one week of online homework assignments; using Ximera content with interactive elements in a course for the first time; resolving approximately 50 GitHub issues; cleaning up a GitHub repository with README, links, and print-ready releases; or adding functionality to the Ximera document class, Cascading Style Sheets, GitHub Actions, Overleaf integration, etc. These activities can be combined and scaled; for example, resolving 500 GitHub issues could justify a \$4,000 award, and adding videos to multiple sections alongside issue resolution could justify \$2,000. The scope of work is not limited to these examples. Flash Grants have also funded AI integration work; notably, Jason Nowell (University of Florida) has used Flash Grant support to incorporate HaLLMos, an LLM-based tool, into Ximera, demonstrating the program's capacity to advance AI-enhanced open educational resources. Flash Grants are paid upon completion of the agreed scope of work and are a proven mechanism: under the current FIPSE award (P116T230012), approximately 80 Flash Grants have been awarded at a rate of roughly 32 per year, directly contributing to growth from 10 to 15 adopting institutions and from 261 to 320 active instructors.

\paragraph{Advisory Board Stipend (\$3,000).} The Advisory Board consists of three members; Neil Soiffer (MathCAT, screen reader software), William Stein (SAGE, open-source mathematics software), and Piotr Mitros (educational technology consultant); who provide guidance on accessibility, sustainability, and technical direction. Each member receives a \$1,000 annual stipend.

\paragraph{AWS Services (\$1,000).} Cloud hosting costs for supplementary Ximera infrastructure, including backup servers and development/testing environments.

\budgetcat{Indirect Costs (\$204,138)}

Indirect costs are calculated at OSU's federally negotiated rate of 57.5\% of modified total direct costs. The rate agreement is approved by the Department of Health and Human Services (DHHS) as the cognizant federal agency. Indirect costs do not apply to permanent equipment, tuition, or subaward amounts exceeding \$25,000.




\budgetcat{Total Year 1: \$559,160 (Direct: \$355,022; Indirect: \$204,138)}
% Total direct + indirect. Must match SF-424A.

\budgetyear{2}
\budgetcat{Personnel (\$64,722)}

\paragraph{Bart Snapp, Principal Investigator} (course release: \$19,796). Dr.\ Snapp receives his second and final course release, reflecting a 3\% cost-of-living adjustment. In Year 2, he will focus on scaling consortium partnerships, continuing refinement of AI-assisted authoring tools, overseeing the Modulus rollout to additional institutions, and coordinating the annual Ximera Workshop.

\paragraph{Jim Fowler, Co-Investigator} (2 months summer: \$30,514). Dr.\ Fowler continues platform development with emphasis on server-side infrastructure for LLM integration and Modulus integration refinements. Summer salary reflects a 3\% increase.

\paragraph{Elizabeth Miller, Evaluator} (\$7,972). Continues data collection with expanded institutional scope. Salary reflects a 3\% increase.

\paragraph{Carolyn Johns, Evaluator} (\$6,440). Continues survey coordination and data management. Salary reflects a 3\% increase.

\budgetcat{Fringe Benefits (\$15,641)}

Calculated at the same federally negotiated rates: off-duty faculty at 15.8\% (\$4,821), regular faculty at 28.3\% (\$5,602), and A\&P staff at 36.2\% (\$5,217).

\budgetcat{Travel (\$46,000)}

Continued support for approximately 23 person-trips at \$2,000 each, covering four major conference exhibitions and one Ximera Workshop. As the consortium expands, travel may increasingly support site visits to new adopting institutions.

\budgetcat{Equipment (\$0)}

\budgetcat{Supplies (\$2,000)}

Replenishment of printed User Manuals, promotional materials, and booth supplies.

\budgetcat{Contractual (\$0)}

\budgetcat{Construction (\$0)}

\budgetcat{Other (\$195,000)}

\paragraph{BAWL --- Jeff Kuan (\$50,000).} Continued accessibility auditing, WCAG compliance verification for new content, and updates to the Best Practices Guide as new interactive element types are introduced.

\paragraph{Infonomic (\$70,000).} With the MVP complete, Year 2 focuses on scaling Modulus deployment across consortium institutions, implementing feedback from Year 1 pilots, and developing the anonymized CSV export schema for cross-institutional research use. Moreover, development must continue on the Modulus Atlas Dissemination Platform. 

\paragraph{Wim Obbels, DevOps (\$12,000).} Continued server infrastructure maintenance at \$1,000/month, with emphasis on supporting new institutional Ximera server deployments.

\paragraph{Paul Zachlin, Dissemination Specialist (\$5,000).} Continued identification and coordination of conference presentation opportunities across the consortium.

% \paragraph{Contract: Alexander Holvoet, User Experience Groups Organizer (\$5,000)}
% Alexander Holvoet is currently a nationally funded PhD-researcher in K12 mathematics education at KU Leuven, one of Ximera's largest stakeholders and an editor of partner Uitwiskeling. Previously he has worked as community manager in EdTech and taught mathematics at secondary and higher education.
% Using his builtup methodological expertise in his PhD, he will manage user experience groups amongst Uitwiskeling's readers in reviewing iteratively designed versions of ATLAS and structuring provided feedback for concrete action points.
% \todo{Add teacher rating of user friendliness as performance measure of ATLAS?}

\paragraph{Flash Grant Stipends (\$54,000).} Continued at the same level, supporting approximately 32 awards per year. In Year 2, Flash Grants will increasingly target content areas beyond mathematics --- including any new disciplines entering the consortium --- and support the conversion of existing PDF-only materials to fully interactive Ximera format.

\paragraph{Advisory Board Stipend (\$3,000).} Continued at \$1,000 per member.

\paragraph{AWS Services (\$1,000).} Continued cloud hosting.

\budgetcat{Indirect Costs (\$185,933)}

Calculated at 57.5\% of modified total direct costs.
\budgetcat{Total Year 2: \$509,296 (Direct: \$323,363; Indirect: \$185,933)}

\budgetyear{3}

\budgetcat{Personnel (\$46,274)}

\paragraph{Jim Fowler, Co-Investigator} (2 months summer: \$31,430). Dr.\ Fowler continues platform development, focusing on long-term sustainability features and documentation of the codebase for community maintenance. Salary reflects a 3\% increase.

\paragraph{Elizabeth Miller, Evaluator} (\$8,211). Expanded analysis responsibilities as the longitudinal dataset matures. Salary reflects a 3\% increase.

\paragraph{Carolyn Johns, Evaluator} (\$6,633). Continued data collection. Salary reflects a 3\% increase.

\textit{Note:} Dr.\ Snapp does not receive a course release in Years 3 or 4. He continues as PI without direct salary support, consistent with his faculty appointment and commitment to the project.

\budgetcat{Fringe Benefits (\$10,340)}

Off-duty faculty at 15.8\% (\$4,966) and A\&P staff at 36.2\% (\$5,374). No regular faculty fringe is incurred in Years 3--4 as there is no course release for Dr.\ Snapp.

\budgetcat{Travel (\$46,000)}

Continued support for approximately 23 person-trips. By Year 3, a portion of travel may support consortium partners presenting at conferences independently, reflecting the project's dissemination maturity.

\budgetcat{Equipment (\$0)}

\budgetcat{Supplies (\$2,000)}

Replenishment of promotional and booth materials.

\budgetcat{Contractual (\$0)}

\budgetcat{Construction (\$0)}

\budgetcat{Other (\$195,000)}

\paragraph{BAWL --- Jeff Kuan (\$50,000).} Continued accessibility work with increasing focus on training consortium authors in accessible content practices and reducing dependence on centralized auditing.

\paragraph{Infonomic (\$70,000).} Continued Modulus maintenance, feature development based on institutional feedback, and support for integration with additional LMS platforms beyond Canvas.

\paragraph{Wim Obbels, DevOps (\$12,000).} Continued infrastructure support at \$1,000/month.

\paragraph{Paul Zachlin, Dissemination Specialist (\$5,000).} Continued conference coordination.

\paragraph{Flash Grant Stipends (\$54,000).} Continued at the same level. Year 3 Flash Grants will emphasize sustainability-oriented work: completing full course conversions, establishing print-on-demand editions, and documenting authoring workflows for long-term community use.

\paragraph{Advisory Board Stipend (\$3,000).} Continued at \$1,000 per member.

\paragraph{AWS Services (\$1,000).} Continued cloud hosting.

\budgetcat{Indirect Costs (\$172,278)}

Calculated at 57.5\% of modified total direct costs.


\budgetcat{Total Year 3: \$471,891 (Direct: \$299,614; Indirect: \$172,278)}

\budgetyear{4}



\budgetcat{Personnel (\$47,662)}

\textbf{Jim Fowler, Co-Investigator} (2 months summer: \$32,372). In the final year, Dr.\ Fowler will focus on ensuring the Ximera platform and Modulus are fully documented and sustainable beyond the grant period. Salary reflects a 3\% increase.

\textbf{Elizabeth Miller, Evaluator} (\$8,458). Final-year data collection and preparation of the summative evaluation dataset. Salary reflects a 3\% increase.

\textbf{Carolyn Johns, Evaluator} (\$6,832). Final-year data collection and reporting. Salary reflects a 3\% increase.

\budgetcat{Fringe Benefits (\$10,650)}

Off-duty faculty at 15.8\% (\$5,115) and A\&P staff at 36.2\% (\$5,535).

\budgetcat{Travel (\$46,000)}

Continued support for approximately 23 person-trips, with emphasis on final dissemination of project results and sustainability planning with consortium partners.

\budgetcat{Equipment (\$0)}

\budgetcat{Supplies (\$2,000)}

Final replenishment of materials.

\budgetcat{Contractual (\$0)}

\budgetcat{Construction (\$0)}

\budgetcat{Other (\$185,000)}

\textbf{BAWL --- Jeff Kuan (\$50,000).} Final-year accessibility work, including completion of the Ximera Accessibility Best Practices Guide and handoff of auditing procedures to trained consortium authors.

\textbf{Infonomic (\$60,000).} Final year of Modulus support at a reduced level, reflecting the product's maturity. Focus on documentation and the Modulus Atlas Dissemination Platform, bug fixes, and ensuring the system is maintainable by the Ximera team beyond the grant period.

\textbf{Wim Obbels, DevOps (\$12,000).} Continued infrastructure support at \$1,000/month, with emphasis on documentation and transition planning for long-term server maintenance.

\textbf{Paul Zachlin, Dissemination Specialist (\$5,000).} Final-year conference coordination and dissemination of project outcomes.

\textbf{Flash Grant Stipends (\$54,000).} In the final year, Flash Grants will prioritize completion and polishing of in-progress textbook projects, ensuring all grant-funded content is publicly available, properly licensed, and archived for long-term access.

\textbf{Advisory Board Stipend (\$3,000).} Continued at \$1,000 per member.

\textbf{AWS Services (\$1,000).} Continued cloud hosting.

\budgetcat{Indirect Costs (\$167,504)}

Calculated at 57.5\% of modified total direct costs.

\budgetcat{Total Year 4: \$458,816 (Direct: \$291,312; Indirect: \$167,504)}




\section{Four-Year Total: \$1,999,164  (Direct: \$1,269,310; Indirect: \$729,853)}
% Must equal SF-424A Section A line 5(e).
\section*{Budget Summary (All Years)}

\renewcommand{\arraystretch}{1.25}
\begin{center}
\begin{tabular}{l r r r r r}
\toprule
\textbf{Category} & \textbf{Year 1} & \textbf{Year 2} & \textbf{Year 3} & \textbf{Year 4} & \textbf{Total} \\
\midrule
Personnel & \$62,837 & \$64,722 & \$46,274 & \$47,662 & \$221,495 \\
Fringe Benefits & \$15,185 & \$15,641 & \$10,340 & \$10,650 & \$51,815 \\
Travel & \$46,000 & \$46,000 & \$46,000 & \$46,000 & \$184,000 \\
Equipment & \$0 & \$0 & \$0 & \$0 & \$0 \\
Supplies & \$6,000 & \$2,000 & \$2,000 & \$2,000 & \$12,000 \\
Contractual & \$0 & \$0 & \$0 & \$0 & \$0 \\
Construction & \$0 & \$0 & \$0 & \$0 & \$0 \\
Other & \$225,000 & \$195,000 & \$195,000 & \$185,000 & \$800,000 \\
\midrule
\textbf{Total Direct} & \textbf{\$355,022} & \textbf{\$323,363} & \textbf{\$299,614} & \textbf{\$291,312} & \textbf{\$1,269,310} \\
Indirect (57.5\%) & \$204,138 & \$185,933 & \$172,278 & \$167,504 & \$729,853 \\
\textbf{Total} & \textbf{\$559,160} & \textbf{\$509,296} & \textbf{\$471,891} & \textbf{\$458,816} & \textbf{\$1,999,164} \\
\bottomrule
\end{tabular}
\end{center}


\end{document}
